\LaTeXe\ guide for the Journal of Functional Programming

### 2019-10-14 papers/jfp/1-intro.tex
Add a TODO

This paper is an extended version of an earlier conference
paper~\cite{mokhov2018buildsystems}. The key changes compared to the earlier
version are: (i) we added further clarifications and examples
into~\S\ref{sec-abstractions}, in particular,~\S\ref{sec-task-examples} is
entirely new; (ii)~\S\ref{sec-scheduler} and~\S\ref{sec-rebuilder} are based on
the material from the conference paper but have been substantially expanded to
include further details and examples, as well as completely new material such
as~\S\ref{sec-step-traces}; (iii)~\S\ref{sec-experience} is completely new; (iv)
\S\ref{sec-failures} and \S\S\ref{sec-polymorphism}-\ref{sec-tracking-aspects}
are almost entirely new, and \S\ref{sec-non-determinism} has been revised.
The new material focuses on our experience and various important practical
considerations, hence justifying the "and Practice" part of the paper title.

>>>>

This paper is an extended version of an earlier conference
paper~\cite{mokhov2018buildsystems}. The key changes compared to the earlier
version are: (i) we added further clarifications and examples
into~\S\ref{sec-abstractions}, in particular,~\S\ref{sec-task-examples} is
entirely new; (ii)~\S\ref{sec-scheduler} and~\S\ref{sec-rebuilder} are based on
the material from the conference paper but have been substantially expanded to
include further details and examples, as well as completely new material such
as~\S\ref{sec-step-traces}; (iii)~\S\ref{sec-experience} is completely new; (iv)
\S\ref{sec-failures} and \S\S\ref{sec-polymorphism}-\ref{sec-tracking-aspects}
are almost entirely new, and \S\ref{sec-non-determinism} has been revised.
The new material focuses on our experience and various important practical
considerations, hence justifying the ``and Practice'' part of the paper title.

### 2019-10-14 papers/jfp/8-engineering.tex
Start working on a revision
Add a TODO

\section{Engineering aspects}\label{sec-engineering}

@@

\subsection{Key-dependent value types}\label{sec-polymorphism}

@@

>>>>

\section{Engineering Aspects}\label{sec-engineering}

@@

\subsection{Key-dependent Value Types}\label{sec-polymorphism}

@@

\subsection{Integration with IDEs}\label{sec-integration-with-ides}

\textbf{TODO:} Neil, could you add 1-2 paragraphs, perhaps with a code snippet
illustrating keys that are pairs of a file and a compilation stage? Perhaps,
you could link to the DAML IDE for an implementation.
